SpatialEpi

### 2021-08-01 README.Rmd
Update README

Note: You may need to install the `cpp11` for all C++ code to compile correctly.

>>>>

Note: In order for all C++ code to compile correctly you may need to

1. Install the `cpp11` package
1. Install an older version of `RcppArmadillo` by running  
    ```{r, eval=FALSE}
    packageurl <- "https://cran.r-project.org/src/contrib/Archive/RcppArmadillo/RcppArmadillo_0.9.900.3.0.tar.gz"
install.packages(packageurl, repos=NULL, type="source")
    ```
